Title

### 2016-11-24 paper.tex
Modified experimental results

%\section{Kernel for structures and Multiple Kernel Learning}
\section{Background}
A kernel method is composed by the following two modules.
A learning algorithm, that expresses the solution only via dot products between training examples.
A kernel function ${k}: \mathcal{X} \times \mathcal{X} \rightarrow \mathbb{R}$ that is a symmetric positive semi-definite function that corresponds to a dot product in a Reproducing Kernel Hilbert Space (RKHS), i.e. there exists a $\phi: \mathcal{X} \rightarrow \mathcal{K} \subseteq \mathbb{R}^D$, where $\mathcal{X}$ is the input space and $\mathcal{K}$ is an Hilbert space (commonly referred to as \textit{feature space}), such that $k(X_i,X_j) = \langle \phi(X_i),\phi(X_j) \rangle$ with $X_i,X_j \in \mathcal{X}$.%~\cite{559923}.
When dealing with structured data, the choice of the kernel to adopt is a key step. Depending on the type of data under consideration, different proposals are available in literature, each one with a different trade-off between predictive performance and computational time (of course, this trade-off depends from the considered task).

@@

\section{Proposed framework}
Often, to work well MKL algorithms require an high number of kernels, and when we use structured data as input, such as graphs, the computational effort to calculate each of them can be high. Moreover each kernel requires an amount of memory that depends on the number of samples, making the MKL approach unpractical when the number of samples and the number of kernels are huge.
In order to avoid these problems, we propose a method to reduce the number of kernels to compute on the complete dataset, based on the robustness of the combination vector $\boldsymbol{\eta}$ when considering just a subset of the available data.\\
In particular if $\boldsymbol{\eta}$, the combination vector learned using the whole set of data and all kernel functions, is similar to the weights vector $\eta_s$ learned using the same kernels calculated on a subset of data, then we can use directly $\eta_s$ in our model.
In this way we can learn quickly the kernels combination, but we have to calculate all kernels anyway.
Furthermore, we can use values in $\eta_s$ to perform a ranking over kernels, removing those below a threshold.
Then we fit the model using only the top kernels selected.

In summary, in the first phase we chose the top kernels using a subset of data, in the latter, we calculate the top kernel matrices using the whole set of data, and then we use them in combination.

\section{Experimental Results (settings?)}
Firstly, we performed some experiments to observe how many samples are required to make $\eta$ and $\eta_s$ similar.
The metric used for comparison is the jaccard similarity score. Indeed, in our context two weights vectors are similar is they provide the same top kernels.
These experiments are summarized in \figurename\ \ref{fig:weights} and \ref{fig:jaccard}.

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{img/weights_GDD.png}
\caption{The weights vector learned by EasyMKL using $50\%$ and $25\%$ of training data. Blue regions represents the comparison with the weights vector calculated using all data.}
\label{fig:weights}
\end{figure}

>>>>

%\section{Kernel for structures and Multiple Kernel Learning}
\section{Background}
A kernel method is composed by the following two modules.
A learning algorithm, that expresses the solution only via dot products between training examples.
A kernel function ${k}: \mathcal{X} \times \mathcal{X} \rightarrow \mathbb{R}$ that is a symmetric positive semi-definite function that corresponds to a dot product in a Reproducing Kernel Hilbert Space (RKHS), i.e. there exists a $\phi: \mathcal{X} \rightarrow \mathcal{K} \subseteq \mathbb{R}^D$, where $\mathcal{X}$ is the input space and $\mathcal{K}$ is an Hilbert space (commonly referred to as \textit{feature space}), such that $k(X_i,X_j) = \langle \phi(X_i),\phi(X_j) \rangle$ with $X_i,X_j \in \mathcal{X}$.%~\cite{559923}.
\textcolor{red}{TODO definire kernel matrix}
When dealing with structured data, the choice of the kernel to adopt is a key step. Depending on the type of data under consideration, different proposals are available in literature, each one with a different trade-off between predictive performance and computational time (of course, this trade-off depends from the considered task).

@@

\section{Proposed framework}
Often, to work well MKL algorithms require an high number of kernels, and when we use structured data as input, such as graphs, the computational effort to calculate each of them can be high. Moreover each kernel requires an amount of memory that depends on the number of samples, making the MKL approach unpractical when the number of samples and the number of kernels are huge.
In order to avoid these problems, we propose a method to reduce the number of kernels to compute on the complete dataset, based on the robustness of the combination vector $\boldsymbol{\eta}$ when considering just a subset of the available data.\\
In particular if $\boldsymbol{\eta}$, the combination vector learned using the whole set of data and all kernel functions, is similar to the weights vector $\hat{\boldsymbol{\eta}}$ learned using the same kernels calculated on a subset of data, we can compute just $\hat{\boldsymbol{\eta}}$ .
%In this way we can learn quickly the kernels combination, but we have to calculate all kernels anyway.
Moreover, we can use the values in $\hat{\boldsymbol{\eta}}$ to perform a ranking over kernels, removing those below a (user-specified) threshold.
Then we compute the kernel matrix, on all the available data, for just the top kernels, and fit a model combining them.

%In summary, in the first phase we choose the top kernels using a subset of the available data. In the second phase, we calculate the top kernel matrices using the whole set of data, and then we use them in combination.

\section{Experimental Assessment}
Firstly, we performed some experiments to observe how many samples are required to make $\eta$ and $\eta_s$ similar.
The metric used for comparison is the jaccard similarity score. Indeed, in our context two weights vectors are similar is they provide the same top kernels.
These experiments are summarized in \figurename\ \ref{fig:weights} and \ref{fig:jaccard}.

% \begin{figure}[!htb]
% \centering
% \includegraphics[width=\textwidth]{img/weights_GDD.png}
% \caption{The weights vector learned by EasyMKL using $50\%$ and $25\%$ of training data. Blue regions represents the comparison with the weights vector calculated using all data.}
% \label{fig:weights}
% \end{figure}
